D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-16 ootavacuous.tex
Update "Future Directions" section
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This paper focuses further on compilers that do only local per-thread
analysis.
Further explorations could consider some classes of global analysis,
for example, analyses that demonstrate that a given expression
will always evaluate to a particular constant.
JMM Causality Test Case 1 discussed in
Appendix~\ref{app:Causality Test Case 1}
provides an example of such a global analysis.

>>>>

This paper focuses primarily on compilers that do only local per-thread
analysis.
Further explorations could consider additional classes of global analysis,
for example, analyses that demonstrate that a given expression will
always evaluate to a particular constant.
JMM Causality Test Case 1 discussed in
Appendix~\ref{app:Causality Test Case 1}
provides an example of such a global analysis.
